ls & Combining Options
        $ ls -l
        drwxr-xr-x 5  cc  eng  4096 Jun 24 16:51  action
        drwxr-xr-x 4  cc  eng  4096 Jun 24 16:51  comedy
        drwxr-xr-x 6  cc  eng  4096 Jun 24 16:51  drama
        -rw-r--r-- 1  cc  eng     0 Jun 24 16:51  genres.txt
    
    The -l option lists files and directories as a table. Here there are four rows, with seven columns separated by spaces. Here’s what each column means:
        1) <<Access rights>>. These indicate the read, write, and execute permissions on the file or directory allowed to the owner, the group, and all users. You can read more about file permissions.
        
        2) <<Number of hard links>. This number counts the number of child directories and files. This number includes the parent directory link (..) and current directory link (.).
        
        3) <<The username of the file’s owner>>. Here the username is cc.

        4) <<The name of the group that owns the file>>. Here the group name is eng.
        
        5) <<The size of the file in bytes>>.


        6) <<The date & time that the file was last modified>>.

        7) <<The name of the file or directory>>.

    In addition to using each option separately, like ls -a or ls -l, multiple options can be used together, like ls -alt. We can group letter options for other commands in the same way.

    ls -alt lists all contents, including hidden files and directories, in long format, ordered by the date and time they were last modified.

Instructions
    1.
    Let’s navigate to the comedy/ directory. Check your current position using pwd, and use a single cd command to get there.

    2.
    Then type
        ls -alt 
    
    To view all files and directories in comedy/, including the hidden ones, in a long table format, sorted by time last modified.