Wildcards
    In addition to using exact filenames as arguments, we can use special characters like <<*>> to select groups of files. These special characters are called <<wildcards>>. For example, here we use cp to <<copy all files in the current working directory into another directory>>.
        cp * my_directory/
    
    Here, <<w*.txt>> selects <<all files in the working directory starting with “w” (prefix) and ending with “.txt” (suffix), and copies them to my_directory/>>.
        cp w*.txt my_directory/
    
    Let’s try out the wildcard symbol in this filesystem!

Instructions
    1.
    We’re back at the root movies/ directory! From here, navigate to the comedy/ directory.

    2.
    In this directory, use the touch command create a new file named shrek.txt. After doing so, list the contents of the current directory.

    3.
    Then, using a wildcard, copy all files in the current directory into the satire/ directory.

    4.
    Without switching directories, look inside the satire/ directory, listing all its contents. You should see a copy of the files the_office.txt and shrek.txt in this directory.

    5.
    Navigate to the action/ directory using this single command:
       cd ../action/ 
    
    Here we navigate up one directory, and then into the action/ directory.

    6.
    Now let’s try using the wildcard * with a prefix and a suffix.

    With a single command, copy all files in the current directory that start with m and end with .txt, to the scifi/ directory.

    7.
    Without switching directories, list all the files and directories in scifi/.

    You should see a copy of all text files starting with "m": matrix.txt, matrix-reloaded.txt, and matrix-revolutions.txt.