Introduction
        A brief overview of the Learn the Command Line course.
What is the Command Line?
        The command line is a <<text interface>> for the computer’s operating system. You can <<use it to traverse and edit your computer’s filesystem>>. Through the command line, you can create new files, edit the contents of those files, delete files, and more!

        We <<access the command line through>> something called <<Bash>>. We’ll go into what that means and how to set it up on your personal device later in the course, but feel free to look ahead now.

What will you learn?
        This course will take you through the <<various functionalities of how to use the command line>>, starting with navigation, and ending with configuring the environment. At any point, you can access the cheatsheet of commands for this course here.

    Navigation
        In this module, you will <<learn how to navigate through a computer’s filesystem solely through the command line>>. You’ll learn how to view the contents of your filesystem, move through the different directories (folders), and make new files and directories.

    Manipulation
        In this module, you will <<learn how to manipulate the contents of the filesystem with the command line>>. You’ll learn how to move files, delete files and directories, and more.

    Redirection
        In this module, you will <<learn how to redirect standard input, standard output, and standard error messages>>. You’ll learn how to display the contents of a file, write to that file, search through directories, and more.

    Configuration
        In this module, you will <<learn how to configure your local environment>>. You’ll learn how to set and edit your settings and preferences, assign aliases (shortcuts), how to use nano, and more.

        Let’s get started!